---
title: "Full_E1_Script"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading in Packages & Creating Folders

```{r}
library(MASS)
library(tidyverse)
library(Hmisc)
library(modelr)
library(scales)
library(gtools)
```

## Generating Correlations

```{r}
number_of_participants = 1

number_of_trials = 30

set.seed(1234)

my_ss <- rep(1:number_of_participants, each = number_of_trials)

my_rs <- rep(runif(number_of_trials, min = 0.2, max = 0.9), number_of_participants)

correlations <- tibble(my_ss = rep(my_ss, each = 6),  my_rs = rep(my_rs, each = 6))
```

## Creating the Residuals Function

```{r}

add_residual_function <- function(my_desired_r) {
  
  set.seed(1234)

  my_sample_size = 128
  
  mean_variable_1 = 0
  sd_variable_1 = 1
  
  mean_variable_2 = 0
  sd_variable_2 = 1
  
  mu <- c(mean_variable_1, mean_variable_2) 
  
  myr <- my_desired_r * sqrt(sd_variable_1) * sqrt(sd_variable_2)
  
  mysigma <- matrix(c(sd_variable_1, myr, myr, sd_variable_2), 2, 2) 
  
  corr_data = as_tibble(mvrnorm(my_sample_size, mu, mysigma, empirical = TRUE))
  
  corr_model <- lm(V2 ~ V1, data = corr_data)
  
  my_residuals <- abs(residuals(corr_model))
  
  data_with_resid <- round(cbind(corr_data, my_residuals), 2)
  
  return(sum(data_with_resid$my_residuals))
  
}
```

## Creating Necessary Components for For Loop

```{r}
r_vec <- correlations$my_rs
res_vec <- c()
```

## Writing For Loop

```{r}
set.seed(1234)

for(value in r_vec) {
  new_value <- add_residual_function(value)
  res_vec <- c(res_vec, new_value) 
}
```

## Concatenating Correlation Data and Residuals 

```{r}
item_no <- rep(1:30, each = 6)
full_data <- cbind(item_no, correlations, res_vec)
```

## Creating Plot: With Encoding

```{r}
set.seed(1234)

my_sample_size = 128

my_desired_r = 0.8

mean_variable_1 = 0
sd_variable_1 = 1

mean_variable_2 = 0
sd_variable_2 = 1

mu <- c(mean_variable_1, mean_variable_2) 

myr <- my_desired_r * sqrt(sd_variable_1) * sqrt(sd_variable_2)

mysigma <- matrix(c(sd_variable_1, myr, myr, sd_variable_2), 2, 2) 

corr_data = as_tibble(mvrnorm(my_sample_size, mu, mysigma, empirical = TRUE))

corr_model <- lm(V2 ~ V1, data = corr_data)

my_residuals <- abs(residuals(corr_model))

data_with_resid <- round(cbind(corr_data, my_residuals), 2)

ggplot(data_with_resid, aes(x = V1, y = V2)) +
  geom_point(aes(alpha = -my_residuals))  +
  #geom_smooth(method = "lm", se = FALSE) +
  labs(x = "", y = "") +
  theme_classic() +
  theme(axis.text = element_blank()) +
  theme(legend.position = "None")

```

## Creating Plot: Without Encoding

```{r}
set.seed(1234)

my_sample_size = 128

my_desired_r = 

mean_variable_1 = 0
sd_variable_1 = 1

mean_variable_2 = 0
sd_variable_2 = 1

mu <- c(mean_variable_1, mean_variable_2) 

myr <- my_desired_r * sqrt(sd_variable_1) * sqrt(sd_variable_2)

mysigma <- matrix(c(sd_variable_1, myr, myr, sd_variable_2), 2, 2) 

corr_data = as_tibble(mvrnorm(my_sample_size, mu, mysigma, empirical = TRUE))

corr_model <- lm(V2 ~ V1, data = corr_data)

my_residuals <- abs(residuals(corr_model))

data_with_resid <- round(cbind(corr_data, my_residuals), 2)

ggplot(data_with_resid, aes(x = V1, y = V2)) +
  geom_point()  +
  #geom_smooth(method = "lm", se = FALSE) +
  labs(x = "", y = "") +
  theme_classic() +
  theme(axis.text = element_blank()) +
  theme(legend.position = "None")
```

## Function for Generating Graphs With Encoding

```{r}
# This function generates plots with the point contrast encoding (Y condition). As the experiment is 3*2, 3 x 30
# plots are needed with the encoding, 30 of each for the small (S), medium (M), and large (L) conditions. This is 
# accomplished by changing the second name argument in the ggsave function. See the comment on line 215 for more 
# detail. NB This chunk must be run again to update the function when changing the size labeling.

plot_generation_with_enc_function <- function(my_desired_r) {
  set.seed(1234)
  
  my_sample_size = 128
  
  mean_variable_1 = 0
  sd_variable_1 = 1
  
  mean_variable_2 = 0
  sd_variable_2 = 1
  
  mu <- c(mean_variable_1, mean_variable_2) 
  
  myr <- my_desired_r * sqrt(sd_variable_1) * sqrt(sd_variable_2)
  
  mysigma <- matrix(c(sd_variable_1, myr, myr, sd_variable_2), 2, 2) 
  
  corr_data = as_tibble(mvrnorm(my_sample_size, mu, mysigma, empirical = TRUE))
  
  corr_model <- lm(V2 ~ V1, data = corr_data)
  
  my_residuals <- abs(residuals(corr_model))
  
  data_with_resid <- round(cbind(corr_data, my_residuals), 2)

test_plot <- ggplot(data_with_resid, aes(x = V1, y = V2)) +
  geom_point(aes(alpha = -my_residuals))  +
  labs(x = "", y = "") +
  theme_classic() +
  theme(axis.text = element_blank()) +
  theme(plot.margin = unit(c(0,0,0,0), "cm")) +
  theme(legend.position = "None")

ggsave(test_plot,filename=paste0(counter, "S", "Y",".png"), # Currently set up to generate graphs labeled "small".
       device = "png",                                      # Change to "M" or "L" as necessary.
       bg = "white",
       path = "all_plots",
       units = "px",
       width = 1200,
       height = 1200,
)

return()
}
```

## For Loop for Plot Generation With Encoding

```{r}
# This loop iterates the function above over the 30 r values in my_rs without the point contrast encoding.

counter = 1
for (value in my_rs) {
  plot_generation_with_enc_function(value)
  if (counter > 0) {
    counter = counter + 1
  }
  }
```

## Function for Generating Graphs Without Encoding

```{r}
# This function generates plots without the point contrast encoding (N condition). As the experiment is 3*2, 3 x 30
# plots are needed without the encoding, 30 of each for the small (S), medium (M), and large (L) conditions. This is 
# accomplished by changing the second name argument in the ggsave function. See the comment on line 283 for more 
# detail. NB This chunk must be run again to update the function when changing the size labeling.

plot_generation_without_enc_function <- function(my_desired_r) {
  set.seed(1234)
  
  my_sample_size = 128
  
  mean_variable_1 = 0
  sd_variable_1 = 1
  
  mean_variable_2 = 0
  sd_variable_2 = 1
  
  mu <- c(mean_variable_1, mean_variable_2) 
  
  myr <- my_desired_r * sqrt(sd_variable_1) * sqrt(sd_variable_2)
  
  mysigma <- matrix(c(sd_variable_1, myr, myr, sd_variable_2), 2, 2) 
  
  corr_data = as_tibble(mvrnorm(my_sample_size, mu, mysigma, empirical = TRUE))
  
  corr_model <- lm(V2 ~ V1, data = corr_data)
  
  my_residuals <- abs(residuals(corr_model))
  
  data_with_resid <- round(cbind(corr_data, my_residuals), 2)

test_plot <- ggplot(data_with_resid, aes(x = V1, y = V2)) +
  geom_point()  +
  labs(x = "", y = "") +
  theme_classic() +
  theme(axis.text = element_blank()) +
  theme(plot.margin = unit(c(0,0,0,0), "cm")) +
  theme(legend.position = "None")

ggsave(test_plot,filename=paste0(counter, "S", "N",".png"), # Currently set up to generate graphs labeled small.
       device = "png",                                      # Change to "M" or "L" as necessary.
       bg = "white",
       path = "all_plots",
       units = "px",
       width = 1200,
       height = 1200,
)

return()
}
```

## Loop for Generating Graphs Without Encoding

```{r}
# This loop iterates the function above over the 30 r values in my_rs without the point contrast encoding.

counter = 1
for (value in my_rs) {
  plot_generation_without_enc_function(value)
  if (counter > 0) {
    counter = counter + 1
  }
  }
```

## Assembling .csv with plot file names, unique item numbers, r values, residuals.

```{r}
images <- mixedsort(list.files(path = "all_plots"))

plot_labels <- rep(c("all_plots/"), each = 180)

plots_with_labels <- paste(plot_labels, images, sep = "")

final_data <- full_data %>%
  select(-c(item_no, my_ss))

unique_item_no <- c(1:180)

instructions <- rep(c(""), each = 180)

data_with_plots <- cbind(unique_item_no, final_data, plots_with_labels, images)
```

## Creating Masks

```{r}
mask_gen_function <- function() {

x <- LETTERS[1:20]
y <- paste0("var", seq(1,20))
data <- expand.grid(X=x, Y=y)
data$Z <- round(runif(400, 0, 1))

mask <- ggplot(data, aes(X, Y, fill= Z)) + 
  geom_tile() +
  scale_fill_gradient(low = "white", high = "black") +
  theme_void() +
  theme(legend.position = "None")

ggsave(mask,filename=paste("mask", counter,".png",sep=""),
       device = "png",
       bg = "white",
       path = "masks",
       units = "px",
       width = 1200,
       height = 1200,)
}

counter = 1
for (i in 1:186) {
  mask_gen_function()
  if (counter > 0) {
    counter = counter + 1
  }
}

masks <- mixedsort(list.files(path = "masks"))

mask_labels <- rep(c("masks/"), each = 186)

masks_with_labels <- paste(mask_labels, masks, sep = "")
```

## Attaching height and width values to each plot, instructions column, and masks vector.

```{r}
size_w <- rep(c(0.86, 0.86, 0.34, 0.34, 0.215, 0.215), times = 30)

size_h <- rep(c(0.86, 0.86, 0.34, 0.34, 0.215, 0.215), times = 30)

data_with_sizes <- cbind(data_with_plots, size_h, size_w, instructions)
```

## Creating attention_check DF.

```{r}
my_rs <- rep(c(0, 1), times = c(3, 3))

res_vec <- rep(c(0), times = 6)

plots_with_labels <- head(plots_with_labels)

images <- head(images)

unique_item_no <- c(181:186)

size_h <- rep(c(0.34), times = 6)

size_w <- rep(c(0.34), times = 6)

instructions <- rep(c("Please ignore the correlation displayed and set the slider to 0.",
                      "Please ignore the correlation displayed and set the slider to 1."),
                    times = c(3, 3))

attention_checks <- cbind(unique_item_no, my_rs, res_vec, plots_with_labels, images,
                          size_h, size_w, instructions)
```

## Creating the final DF by rbinding attention_checks with data_with_sizes.

```{r}
E1_full_data <- rbind(data_with_sizes, attention_checks) %>%
  cbind(masks_with_labels)

write.csv(E1_full_data, "E1_full_data.csv", row.names = FALSE)
```

## Practice Trials

```{r}
dir.create("practice_plots")

number_of_participants = 1

number_of_trials = 2

set.seed(12345)

my_ss <- rep(1:number_of_participants, each = number_of_trials)

my_rs <- rep(runif(number_of_trials, min = 0.2, max = 0.9), number_of_participants)

correlations <- tibble(my_ss, my_rs)
```


```{r}
practice_plot_generation_without_enc_function <- function(my_desired_r) {
  set.seed(1234)
  
  my_sample_size = 128
  
  mean_variable_1 = 0
  sd_variable_1 = 1
  
  mean_variable_2 = 0
  sd_variable_2 = 1
  
  mu <- c(mean_variable_1, mean_variable_2) 
  
  myr <- my_desired_r * sqrt(sd_variable_1) * sqrt(sd_variable_2)
  
  mysigma <- matrix(c(sd_variable_1, myr, myr, sd_variable_2), 2, 2) 
  
  corr_data = as_tibble(mvrnorm(my_sample_size, mu, mysigma, empirical = TRUE))
  
  corr_model <- lm(V2 ~ V1, data = corr_data)
  
  my_residuals <- abs(residuals(corr_model))
  
  data_with_resid <- round(cbind(corr_data, my_residuals), 2)

test_plot <- ggplot(data_with_resid, aes(x = V1, y = V2)) +
  geom_point()  +
  labs(x = "", y = "") +
  theme_classic() +
  theme(axis.text = element_blank()) +
  theme(plot.margin = unit(c(0,0,0,0), "cm")) +
  theme(legend.position = "None")

ggsave(test_plot,filename=paste0(counter,"P",".png"), 
       device = "png",
       bg = "white",
       path = "practice_plots",
       units = "px",
       width = 1200,
       height = 1200,
)

return()
}
```

```{r}

counter = 1
for (value in my_rs) {
  practice_plot_generation_without_enc_function(value)
  if (counter > 0) {
    counter = counter + 1
  }
  }
```

```{r}
practice_images <- mixedsort(list.files(path = "practice_plots"))

size_h_p <- rep(c(0.34), times = 2)

size_w_p <- rep(c(0.34), times = 2)

practice_data <- cbind(practice_images, size_h_p, size_w_p)

write.csv(practice_data, "practice_plots.csv", row.names = FALSE)
```









